---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# missingDetect

<!-- badges: start -->
<!-- badges: end -->

The goal of missingDetect is to calculate the proportion of missing values for each column,and output the result of columns having NA existed.

## Installation

missingDetect is not yet on CRAN. But, you can download it from this repository using the following R command:

``` r
devtools::install_github("Rpackage_MenghongHuang/missingDetect")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2021/Rpackage_MenghongHuang")
```
## Example

This is a basic example which shows you how to detect data missing problems of a tibble dataset:

```{r example}
library(missingDetect)
missing_prop_detect(palmerpenguins::penguins)
```

This package is special because it also works on a input of dataframe:

```{r cars}
df<- as.data.frame(palmerpenguins::penguins)
missing_prop_detect(df)
```

