---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rpackage.missingDetect

<!-- badges: start -->

Title: Detect the proportion of missing values in columns of tibble/dataframe

Version: 0.1.0

<!-- badges: end -->

The goal of `Rpackage.missingDetect` is to calculate the proportion of missing values for each column in a dataset and output the result of columns having NA existed.

## Installation

`Rpackage.missingDetect` is not yet on CRAN. You can download this development version from [GitHub](https://github.com/) using the following R command:

``` r
devtools::install_github("stat545ubc-2021/Rpackage.missingDetect")
```

## Example

This is a basic example which shows you how to detect data missing problems of a tibble dataset:

```{r example}
library(Rpackage.missingDetect)
missing_prop_detect(palmerpenguins::penguins)
```

This package can also work on a input of dataframe:

```{r cars}
df<- as.data.frame(palmerpenguins::penguins)
missing_prop_detect(df)
```

